---
title: "TJ's Notebook"
output:
  html_document:
    df_print: paged
  html_notebook: default
  pdf_document: default
---

```{r message = F}
library(tidyverse)
library(devtools)
install_github("nxskok/smmr")
library(smmr)
library(PMCMRplus)
```

a)
```{r}
MyData <- read_excel("Canadian_Equity_Funds.xls")
MyData
```
Here we can see there are 60 rows of data, and 10 variables.

b)
```{r}
NewData = drop_na(MyData, Assets)
NewData
```
All the null values have been removed from the table and theres now 54 rows of data instead of 60.

c)
```{r}
ggplot(NewData, aes(x = Assets)) + geom_histogram(bins = 10)
```
A sign test for the median is better since there would be an equal amount of values on both sides of the median, whereas a t-test would be centered around the mean which would take the average of the values.

d)
```{r}
above = 0
below = 0

for (asset in NewData$Assets){
  if (asset > 55){
    above = above + 1
  }
  else if (asset < 55){
    below = below + 1
  }
}

above
below
```
I would expect a sign test to reject the null median of 55 since there more than double the values are below 55 then above. Therefore, the null meadian from a sign test should be lower.

e)
```{r}
sign_test(NewData, Assets, 55)
```


f)
```{r}
ci_median(NewData, Assets)
```
The value 55 is outside of the 95% CI.
