---
title: "TJ's Notebook"
output:
  html_document:
    df_print: paged
  html_notebook: default
  pdf_document: default
---

```{r message = F}
library(tidyverse)
library(devtools)
install_github("nxskok/smmr")
library(smmr)
```

a)
```{r}
MyData <- read_csv("moon.csv")
MyData
```

b)

This is a matched pair experiment since the independent variable `patient` has 2 dependant variables(`moonday` and `otherday`) associated with it. Therefore, each x-value will be associated with 2 y-values.

c)
```{r}
ggplot(MyData, aes(x = patient, y = (moonday - otherday))) + geom_point()
```

The principal assumption is that the difference of the matched pairs follow a normal distribution.

d)
```{r}
with(MyData, t.test(moonday, otherday, paired = T))
```
The differences of `moonday` and `otherday` are between 1.623968 and 3.241365, with the mean of the difference being 2.432667. Since the p-value is below 0.05, we reject the null hypothesis.

e)
```{r}
MyData %>% mutate(MyDiff = moonday - otherday) %>%
sign_test(MyDiff, 0)
```
Since we are testing for higher aggressive behaviour on days closer to a full moon, we use the upper p-value. Since the upper p-value is 0.0004882812 and is less than 0.05, we reject the null hypothesis.

f)

A signed test is better since the scatterplot graph shows that the difference between moonday and otherday isn't normally distributed since there are outliers. Therefore, we shouldn't use a t-test, and use a sign test instead.

