---
title: "Assignment 3"
output:
  html_document:
    df_print: paged
  html_notebook: default
  pdf_document: default
---

```{r message = F}
library(tidyverse)
```

a)
```{r}
heads <- 80
coin_tosses <- 125

prop.test(heads, coin_tosses)
```
Since the p-value is less than 0.05, we reject the null hypothesis and conclude that the coin is biased in favour of heads.

b)
```{r}
heads <- 73
coin_tosses <- 125
p <- 0.5
alternative <- "greater"

prop.test(heads, coin_tosses, p, alternative)
```
Through trial and error, the coin must show heads atleast 73 times out of 125 coin tosses to reject H0: p=0.5 in favour of Ha: p>0.5 since the C.I. then has a lower bound of p>0.5.

c)
```{r}
n <- 4
p <- 0.3
i <- 1

while (i <= 10){
  r = rbinom(i, n, p)
  print(r)
  i = i + 1
}
```
From the 10 random samples, We can conclude that the trials are between 0 and the specified value with a probablility of each number showing up as p=0.3 and the amount of trials are n=4. rbinom seems to simulate the outcome of random bernoulli trials.

d)
```{r}
n <- 125
p <- 0.6
mean <- n*p
sd <- sqrt(n*p*(1-p))

my.sample = function()
  {
  r = rnorm(n, mean, sd)
  t = t.test(r, mu = 75)
  t$p.value < 0.05
}

simulation = replicate(100, my.sample())
count = table(simulation)
power = count/n

count
power
```
From the "simulation" we can see that the estimate for the power of the z-test is 0.104 for a proportion to reject H0: p=0.5 in favour of Ha: p>0.5 when the probability is 0.6.

